---
title: "Spin-within combination model"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)

library(tidyverse)
library(ggthemes)
library(jsonlite)
library(readxl)
library(tidyboot)
#library(GGally)
library(coda)
library(data.table)


estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

```


```{r}
data <- read_csv("../data/merged_data.csv")
```

# Base Model

```{r}
model <-  bind_rows(
  fread("../model/output/spin-within_model_slope_variance_prediction-2000_burn2000_lag0_chain1.csv"),
  fread("../model/output/spin-within_model_slope_variance_prediction-2000_burn2000_lag0_chain2.csv")
)%>%
  mutate(chain = as.character(chain))#%>%saveRDS("../model/output/comb_model.rds")

#model <- readRDS("../model/output/comb_model.rds")
```

## Combination prediction

```{r}
prediction <- model %>%
  filter(a == "prediction")%>%
  select(-a,-b, -g)%>%
  rename(condition = c,
         familiar = d, 
         subid = e,
         pred = f)%>%
  group_by(condition,familiar, subid)%>%
  summarise(model_pred = estimate_mode(pred),
            model_lci = hdi_lower(pred),
            model_uci = hdi_upper(pred))%>%
  left_join(data %>% select(condition,familiar,subid, correct))%>%
  ungroup()%>%
  mutate(bin_pred = round(model_pred),
         match = ifelse(bin_pred == correct, 1, 0))%>%
  group_by(correct, bin_pred)%>%
  summarise(freq = n())%>%
  group_by(correct)%>%
  mutate(corrects = sum(freq),
         hit_rate = freq/corrects)
  
ggplot(prediction, aes(x = factor(correct), y = factor(bin_pred), fill = hit_rate))+
  geom_tile(aes(width=1, height=1),alpha = .75, col = "black", size = 1)+
  labs(x = "Data", y= "Model")+
  theme_minimal()+
  scale_fill_viridis_c(begin = 0, end = 1, name = "Frequency")

```

```{r}
chance <- model %>%
  filter(a == "prediction")%>%
  select(-a,-b, -g)%>%
  rename(condition = c,
         familiar = d, 
         subid = e,
         pred = f)%>%
  group_by(chain,condition,familiar, subid)%>%
  summarise(model_pred = estimate_mode(pred),
            model_lci = hdi_lower(pred),
            model_uci = hdi_upper(pred))%>%
  left_join(data %>% select(condition,familiar,subid, correct))%>%
  ungroup()%>%
  mutate(bin_pred = round(model_pred),
         match = ifelse(bin_pred == correct, 1, 0))%>%
  group_by(chain)%>%
  tidyboot_mean(col = match)

ggplot(chance, aes(x = chain, y = mean))+
  geom_hline(yintercept = 0.5, lty = 2, alpha = .5)+
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper))+
  ylim(0,1)+
  theme_minimal()


```



## Production probability

```{r}
model%>%
  filter(c == "successful_production_probability")%>%
  rename(value = f)%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  scale_fill_colorblind()+
  xlim(0,1)+
  theme_minimal()
```

## Speaker optimality

### overall intercept, slope and sigma

```{r}
model%>%
  filter(c == "speaker_optimality", 
         b != "parameters")%>%
  rename(parameter = b,
         value = f)%>%
  mutate(parameter = factor(parameter, levels = c("intercept", "slope", "sigma")))%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(~parameter)+
  scale_fill_colorblind()+
  xlim(-4,4)+
  theme_minimal()
```


### by subject

```{r}
model%>%
  rename(type = b,
         parameter = c,
         subject = e, 
         speaker_optimality = f)%>%
  filter(type != "sigma",
         parameter == "speaker_optimality")%>%
  ggplot(., aes(x = speaker_optimality, fill = chain))+
  geom_density(alpha = .5)+
  facet_wrap(subject~., scales = "free_y")+
  scale_fill_colorblind()+
  theme_minimal()
```


## Semantic knowledge

### overall intercept, slope and sigma

```{r}
model%>%
  filter(c == "semantic_knowledge", 
         b != "parameters")%>%
  rename(parameter = b,
         value = f)%>%
  mutate(parameter = factor(parameter, levels = c("intercept", "slope", "sigma")))%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(~parameter)+
  scale_fill_colorblind()+
  xlim(-4,4)+
  theme_minimal()
```

### by subject

```{r}
model%>%
  rename(parameter = c,
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(familiar),
         parameter == "semantic_knowledge", 
         familiar == "lock")%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  ggtitle("Seamntic knowledge for 'lock'")+
  facet_wrap(subject~., scales = "free_y")+
  scale_fill_colorblind()+
  theme_minimal()
```

### by item

```{r}
model%>%
  rename(parameter = c,
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(familiar),
         !is.na(value),
         parameter == "semantic_knowledge")%>%
  group_by(subject, familiar,chain)%>%
    summarise(mode = estimate_mode(value),
            lci = hdi_lower(value),
            uci = hdi_upper(value))%>%
  ggplot(., aes(x = factor(subject), y= mode, col = chain))+
  geom_pointrange(aes(ymin = lci, ymax = uci), position = position_dodge(width = .1), pch = 4)+
  scale_color_colorblind()+
  facet_grid(familiar~.)+
  theme_few()

model%>%
  rename(parameter = c,
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(familiar),
         !is.na(value),
         parameter == "semantic_knowledge")%>%
  group_by(subject, familiar,chain)%>%
    summarise(mode = estimate_mode(value),
            lci = hdi_lower(value),
            uci = hdi_upper(value))%>%
  ggplot(., aes(x = familiar, y= mode, col = factor(subject)))+
  geom_pointrange(aes(ymin = lci, ymax = uci), position = position_dodge(width = .1), pch = 4)+
  scale_color_viridis_d()+
  facet_grid(chain~.)+
  theme_few()
```

## Prior sensitivity

### overall intercept, slope and sigma

```{r}
model%>%
  filter(c == "prior", 
         b != "parameters")%>%
  rename(parameter = b,
         value = f)%>%
  mutate(parameter = factor(parameter, levels = c("intercept", "slope", "sigma")))%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(~parameter)+
  scale_fill_colorblind()+
  xlim(-4,4)+
  theme_minimal()
```

### by subject

```{r}
model%>%
  rename(parameter = c, 
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(subject),
         parameter == "prior")%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_wrap(subject~., scales = "free_y")+
  scale_fill_colorblind()+
  xlim(0,1)+
  theme_minimal()

```

# Comptence Model

```{r}
item_model <-  bind_rows(
  fread("../model/output/spin-within_model_item_slope-40000_burn100000_lag4_chain1.csv")%>%mutate(chain = "1"),
  fread("../model/output/spin-within_model_item_slope-40000_burn100000_lag4_chain2.csv")%>%mutate(chain = "2"),
  fread("../model/output/spin-within_model_item_slope-40000_burn100000_lag4_chain3.csv")%>%mutate(chain = "3")
)%>%saveRDS("../model/output/model_run_item_slopes.rds")


item_model <- readRDS("../model/output/model_run_item_slopes.rds")
```


## Production probability

```{r}
item_model%>%
  filter(c == "successful_production_probability")%>%
  rename(value = f)%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  scale_fill_colorblind()+
  xlim(0,1)+
  theme_minimal()
```

## Speaker optimality

### overall intercept, slope and sigma

```{r}
item_model%>%
  filter(c == "speaker_optimality", 
         b != "parameters")%>%
  rename(parameter = b,
         value = f)%>%
  mutate(parameter = factor(parameter, levels = c("intercept", "slope", "sigma")))%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(~parameter)+
  scale_fill_colorblind()+
  xlim(-4,4)+
  theme_minimal()
```


### by subject

```{r}
item_model%>%
  rename(type = b,
         parameter = c,
         subject = e, 
         speaker_optimality = f)%>%
  filter(type != "sigma",
         parameter == "speaker_optimality")%>%
  ggplot(., aes(x = speaker_optimality, fill = chain))+
  geom_density(alpha = .5)+
  facet_wrap(~subject, scales = "free_y")+
  scale_fill_colorblind()+
  theme_minimal()
```


## Semantic knowledge

### overall intercept, slope

```{r}
item_model%>%
  filter(c == "semantic_knowledge", 
         b != "parameters", 
         d != "intercept",
         d != "slope")%>%
  rename(parameter = b,
         value = f)%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(~parameter)+
  scale_fill_colorblind()+
  xlim(-4,4)+
  theme_minimal()
```

### overall sigmas

```{r}
item_model%>%
  filter(c == "semantic_knowledge", 
         b != "parameters", 
         b == "sigma")%>%
  rename(parameter = d,
         value = g)%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(~parameter)+
  scale_fill_colorblind()+
  xlim(-4,4)+
  theme_minimal()
```

### subhect sigmas

```{r}
item_model%>%
  filter(c == "semantic_knowledge", 
         b == "sigma", 
         d == "subject")%>%
  rename(parameter = d,
         value = g)%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(~parameter)+
  scale_fill_colorblind()+
  xlim(-4,4)+
  theme_minimal()
```

### by subject

```{r}
item_model%>%
  rename(parameter = c,
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(familiar),
         parameter == "semantic_knowledge", 
         familiar == "lock")%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_wrap(~subject, scales = "free_y")+
  ggtitle("Semantic knowledge for lock")+
  scale_fill_colorblind()+
  theme_minimal()
```

### by item

```{r}
item_model%>%
  rename(parameter = c,
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(familiar),
         !is.na(value),
         parameter == "semantic_knowledge")%>%
  group_by(subject, familiar,chain)%>%
    summarise(mode = estimate_mode(value),
            lci = hdi_lower(value),
            uci = hdi_upper(value))%>%
  ggplot(., aes(x = factor(subject), y= mode, col = chain))+
  geom_pointrange(aes(ymin = lci, ymax = uci), position = position_dodge(width = .1), pch = 4)+
  scale_color_colorblind()+
  facet_grid(familiar~.)+
  theme_few()

item_model%>%
  rename(parameter = c,
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(familiar),
         !is.na(value),
         parameter == "semantic_knowledge")%>%
  group_by(subject, familiar,chain)%>%
    summarise(mode = estimate_mode(value),
            lci = hdi_lower(value),
            uci = hdi_upper(value))%>%
  ggplot(., aes(x = familiar, y= mode, col = factor(subject)))+
  geom_pointrange(aes(ymin = lci, ymax = uci), position = position_dodge(width = .1), pch = 4)+
  scale_color_viridis_d()+
  facet_grid(chain~.)+
  theme_few()
```
## Prior sensitivity

### overall intercept, slope and sigma

```{r}
item_model%>%
  filter(c == "prior", 
         b != "parameters")%>%
  rename(parameter = b,
         value = f)%>%
  mutate(parameter = factor(parameter, levels = c("intercept", "slope", "sigma")))%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(~parameter)+
  scale_fill_colorblind()+
  xlim(-4,4)+
  theme_minimal()
```

### by subject

```{r}
item_model%>%
  rename(parameter = c, 
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(subject),
         parameter == "prior")%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_wrap(~subject, scales = "free_y")+
  scale_fill_colorblind()+
  xlim(0,1)+
  theme_minimal()

```

## Relations between models and data

Here are some simple correlations between the model estimates and the data.

### Speaker Optimality and ME Data

There shouldn't be a 1:1 correspondence (i.e. very high correlation) because the ME task also -- and critically -- involves semantic knowledge

```{r}
sgm <- gauss_model%>%
  rename(type = b,
         parameter = c,
         subject = e, 
         value = f)%>%
  filter(type != "sigma",
         parameter == "speaker_optimality")%>%
  mutate(subject = factor(subject))%>%
  group_by(subject)%>%
  summarise(mode = estimate_mode(value),
            lci = hdi_lower(value),
            uci = hdi_upper(value))%>%
  mutate(model = "gaussian")

scm <- comp_model%>%
  rename(type = b,
         parameter = c,
         subject = e, 
         value = f)%>%
  filter(type != "sigma",
         parameter == "speaker_optimality")%>%
  mutate(subject = factor(subject))%>%
  group_by(subject)%>%
  summarise(mode = estimate_mode(value),
            lci = hdi_lower(value),
            uci = hdi_upper(value))%>%
  mutate(model = "competence")

sd <- data%>%
  filter(task == "mutual_exclusivity")%>%
    mutate(subject = factor(subid))%>%
    group_by(subject)%>%
    summarise(data_mean = mean(correct))%>%
  filter(!is.na(data_mean))

bind_rows(
  sgm%>%left_join(sd),
  scm%>%left_join(sd)
)%>%
  ggplot(aes(x = mode, y = data_mean))+
  geom_point(alpha = .5)+
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mode, y = data_mean, label = paste(..r.label..)), inherit.aes = F, size = 4, r.accuracy = 0.01, cor.coef.name = "r")+
  facet_grid(~model)+
  theme_minimal()+
  geom_smooth(method = "lm", se = F, col = "black")+
  ylim(0,1)
```

### Semantic knowledge and comprehension / production data

Note that the model estimates also take in the ME data

```{r}
semgm <- gauss_model%>%
  rename(parameter = c,
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(familiar),
         !is.na(value),
         parameter == "semantic_knowledge")%>%
  mutate(subject = factor(subject))%>%
  group_by(familiar, subject)%>%
  summarise(mode = estimate_mode(value),
            lci = hdi_lower(value),
            uci = hdi_upper(value))%>%
  mutate(model = "gaussian")

semcm <- comp_model%>%
  rename(parameter = c,
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(familiar),
         !is.na(value),
         parameter == "semantic_knowledge")%>%
  mutate(subject = factor(subject))%>%
  group_by(familiar, subject)%>%
  summarise(mode = estimate_mode(value),
            lci = hdi_lower(value),
            uci = hdi_upper(value))%>%
  mutate(model = "competence")

semd <- data%>%
  filter(task == "comprehension" | task == "production" 
         #| task == "mutual_exclusivity"
         )%>%
    mutate(subject = factor(subid))%>%
    group_by(familiar,subject)%>%
    summarise(data_mean = mean(correct))

bind_rows(
  semgm%>%left_join(semd),
  semcm%>%left_join(semd)
)%>%
  ggplot(aes(x = mode, y = data_mean))+
    geom_abline(intercept = 0, slope = 1, lty = 2, alpha = .5)+
  geom_point(alpha = .5)+
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mode, y = data_mean, label = paste(..r.label..)), inherit.aes = F, size = 4, r.accuracy = 0.01, cor.coef.name = "r")+
  facet_grid(~model)+
  theme_minimal()+
  ylim(0,1)+
  xlim(0,1)
```

### Prior

Here we have a pretty good 1:1 correspondence and should see high correlations. 

```{r}
pgm <- gauss_model%>%
  rename(parameter = c, 
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(subject),
         parameter == "prior")%>%
  mutate(subject = factor(subject))%>%
  group_by(subject)%>%
  summarise(mode = estimate_mode(value),
            lci = hdi_lower(value),
            uci = hdi_upper(value))%>%
  mutate(model = "gaussian")

pcm <- comp_model%>%
  rename(parameter = c, 
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(subject),
         parameter == "prior")%>%
  mutate(subject = factor(subject))%>%
  group_by(subject)%>%
  summarise(mode = estimate_mode(value),
            lci = hdi_lower(value),
            uci = hdi_upper(value))%>%
  mutate(model = "competence")

pd <- data%>%
    filter(task == "novelty")%>%
    mutate(subject = factor(subid))%>%
    group_by(subject)%>%
    summarise(data_mean = mean(correct))%>%
  filter(!is.na(data_mean))

bind_rows(
  pgm%>%left_join(pd),
  pcm%>%left_join(pd)
)%>%
  ggplot(aes(x = mode, y = data_mean))+
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = .5)+
  geom_point(alpha = .5)+
  stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = mode, y = data_mean, label = paste(..r.label..)), inherit.aes = F, size = 4, r.accuracy = 0.01, cor.coef.name = "r")+
  facet_grid(~model)+
  theme_minimal()+
  ylim(0,1)+
  xlim(0,1)
    
```

