---
title: "Spin-within model output"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)

library(tidyverse)
library(ggthemes)
library(jsonlite)
library(readxl)
library(tidyboot)
#library(GGally)
library(coda)
library(data.table)


estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}

hdi_upper<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}

```

# Comprehension

```{r}
data <- read_csv("../data/merged_data.csv")
```

# Descriptives

```{r}
data%>%
  group_by(task)%>%
  summarise(N = length(unique(subid)))
```


# Model Output

```{r}
model <-  bind_rows(
  fread("../model/output/spin-within_model-10000_burn100000_lag4_chain1.csv")%>%mutate(chain = "1"),
  fread("../model/output/spin-within_model-10000_burn100000_lag4_chain2.csv")%>%mutate(chain = "2"),
  fread("../model/output/spin-within_model-10000_burn100000_lag4_chain3.csv")%>%mutate(chain = "3")
)%>%saveRDS("../model/output/model_run.rds")

model <- readRDS("../model/output/model_run.rds")
```

# Production probability

```{r}
model%>%
  filter(c == "successful_production_probability")%>%
  rename(value = f)%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  scale_fill_colorblind()+
  xlim(0,1)+
  theme_minimal()
```

# Speaker optimality

## overall intercept, slope and sigma

```{r}
model%>%
  filter(c == "speaker_optimality", 
         b != "parameters")%>%
  rename(parameter = b,
         value = f)%>%
  mutate(parameter = factor(parameter, levels = c("intercept", "slope", "sigma")))%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(~parameter)+
  scale_fill_colorblind()+
  xlim(-4,4)+
  theme_minimal()
```


## by subject

```{r}
model%>%
  rename(type = b,
         parameter = c,
         subject = e, 
         speaker_optimality = f)%>%
  filter(type != "sigma",
         parameter == "speaker_optimality")%>%
  ggplot(., aes(x = speaker_optimality, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(subject~., scales = "free_y")+
  scale_fill_colorblind()+
  theme_minimal()
```


# Semantic knowledge

## overall intercept, slope and sigma

```{r}
model%>%
  filter(c == "semantic_knowledge", 
         b != "parameters")%>%
  rename(parameter = b,
         value = f)%>%
  mutate(parameter = factor(parameter, levels = c("intercept", "slope", "sigma")))%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(~parameter)+
  scale_fill_colorblind()+
  xlim(-4,4)+
  theme_minimal()
```

## by subject

```{r}
model%>%
  rename(parameter = c,
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(familiar),
         parameter == "semantic_knowledge", 
         familiar == "sieve")%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(subject~., scales = "free_y")+
  scale_fill_colorblind()+
  theme_minimal()
```

by item

```{r}
model%>%
  rename(parameter = c,
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(familiar),
         parameter == "semantic_knowledge")%>%
  group_by(subject, familiar,chain)%>%
    summarise(mode = estimate_mode(value),
            lci = hdi_lower(value),
            uci = hdi_upper(value))%>%
  ggplot(., aes(x = familiar, y= mode, col = chain))+
  geom_pointrange(aes(ymin = lci, ymax = uci), position = position_dodge(width = .5), pch = 4)+
  scale_color_colorblind()+
  facet_wrap(~subject)+
  theme_few()
```

# Prior sensitivity

## overall intercept, slope and sigma

```{r}
model%>%
  filter(c == "prior", 
         b != "parameters")%>%
  rename(parameter = b,
         value = f)%>%
  mutate(parameter = factor(parameter, levels = c("intercept", "slope", "sigma")))%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(~parameter)+
  scale_fill_colorblind()+
  xlim(-4,4)+
  theme_minimal()
```

## by subject

```{r}
model%>%
  rename(parameter = c, 
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(subject),
         parameter == "prior")%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(subject~.)+
  scale_fill_colorblind()+
  xlim(0,1)+
  theme_minimal()

```

# Item slope model

```{r}
item_model <-  bind_rows(
  fread("../model/output/spin-within_model_item_slope-20000_burn50000_lag4_chain1.csv")%>%mutate(chain = "1"),
  fread("../model/output/spin-within_model_item_slope-20000_burn50000_lag4_chain2.csv")%>%mutate(chain = "2"),
  fread("../model/output/spin-within_model_item_slope-20000_burn50000_lag4_chain3.csv")%>%mutate(chain = "3")
)%>%saveRDS("../model/output/model_run_item_slopes.rds")


item_model <- readRDS("../model/output/model_run_item_slopes.rds")
```


## Production probability

```{r}
item_model%>%
  filter(c == "successful_production_probability")%>%
  rename(value = f)%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  scale_fill_colorblind()+
  xlim(0,1)+
  theme_minimal()
```

## Speaker optimality

### overall intercept, slope and sigma

```{r}
item_model%>%
  filter(c == "speaker_optimality", 
         b != "parameters")%>%
  rename(parameter = b,
         value = f)%>%
  mutate(parameter = factor(parameter, levels = c("intercept", "slope", "sigma")))%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(~parameter)+
  scale_fill_colorblind()+
  xlim(-4,4)+
  theme_minimal()
```


### by subject

```{r}
item_model%>%
  rename(type = b,
         parameter = c,
         subject = e, 
         speaker_optimality = f)%>%
  filter(type != "sigma",
         parameter == "speaker_optimality")%>%
  ggplot(., aes(x = speaker_optimality, fill = chain))+
  geom_density(alpha = .5)+
  facet_wrap(~subject, scales = "free_y")+
  scale_fill_colorblind()+
  theme_minimal()
```


## Semantic knowledge

### overall intercept, slope

```{r}
item_model%>%
  filter(c == "semantic_knowledge", 
         b != "parameters", 
         b != "sigma")%>%
  rename(parameter = b,
         value = f)%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(~parameter)+
  scale_fill_colorblind()+
  xlim(-4,4)+
  theme_minimal()
```

### overall sigmas

```{r}
item_model%>%
  filter(c == "semantic_knowledge", 
         b != "parameters", 
         b == "sigma")%>%
  rename(parameter = d,
         value = g)%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(~parameter)+
  scale_fill_colorblind()+
  xlim(-4,4)+
  theme_minimal()
```

### by subject

```{r}
item_model%>%
  rename(parameter = c,
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(familiar),
         parameter == "semantic_knowledge", 
         familiar == "lock")%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_wrap(~subject, scales = "free_y")+
  ggtitle("Semantic knowledge for lock")+
  scale_fill_colorblind()+
  theme_minimal()
```

### by item

```{r}
item_model%>%
  rename(parameter = c,
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(familiar),
         !is.na(value),
         parameter == "semantic_knowledge")%>%
  group_by(subject, familiar,chain)%>%
    summarise(mode = estimate_mode(value),
            lci = hdi_lower(value),
            uci = hdi_upper(value))%>%
  ggplot(., aes(x = factor(subject), y= mode, col = chain))+
  geom_pointrange(aes(ymin = lci, ymax = uci), position = position_dodge(width = .1), pch = 4)+
  scale_color_colorblind()+
  facet_grid(familiar~.)+
  theme_few()

item_model%>%
  rename(parameter = c,
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(familiar),
         !is.na(value),
         parameter == "semantic_knowledge")%>%
  group_by(subject, familiar,chain)%>%
    summarise(mode = estimate_mode(value),
            lci = hdi_lower(value),
            uci = hdi_upper(value))%>%
  ggplot(., aes(x = familiar, y= mode, col = factor(subject)))+
  geom_pointrange(aes(ymin = lci, ymax = uci), position = position_dodge(width = .1), pch = 4)+
  scale_color_viridis_d()+
  facet_grid(chain~.)+
  theme_few()
```
## Prior sensitivity

### overall intercept, slope and sigma

```{r}
item_model%>%
  filter(c == "prior", 
         b != "parameters")%>%
  rename(parameter = b,
         value = f)%>%
  mutate(parameter = factor(parameter, levels = c("intercept", "slope", "sigma")))%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_grid(~parameter)+
  scale_fill_colorblind()+
  xlim(-4,4)+
  theme_minimal()
```

### by subject

```{r}
item_model%>%
  rename(parameter = c, 
         familiar = d, 
         subject = e, 
         value = f)%>%
  filter(!is.na(subject),
         parameter == "prior")%>%
  ggplot(., aes(x = value, fill = chain))+
  geom_density(alpha = .5)+
  facet_wrap(~subject, scales = "free_y")+
  scale_fill_colorblind()+
  xlim(0,1)+
  theme_minimal()

```


